\section{Experience}
\begin{entrylist}

  \entry
    {04/09-07/09}
    {Development Assistant}
		{Genesky Bio-Tech Co, Ltd., Shanghai, China}
		{
			\begin{tightemize}
				\item{Built up T-vector cloning platform, performed PCR with genomic DNA isolated
					from clinical samples.}
				\item{Analyzed genotypes according to sequencing results and composed the report
					sent to clients, like academic labs and clinics.}
			\end{tightemize}
		}

  \entry
    {07/08-08/08}
		{Summer Research Intership}
    {China Novartis Institues for BioMedical Research}
		{
			\begin{tightemize}
				\item{Identified and isolated mutant cancer cell gene targets and determined
					receptor function by transient transfection.}
				\item{Assisted nude mice model experiments.}
			\end{tightemize}
		}

    \entry
    {07/12-09/12}
		{Hospital Volunteer}
		{Lourdes Hospital, Binghamton, NY}
    {
			\begin{tightemize}
				\item{Served in emergency room and hospital.}
				\item{Familiarized with procedures in emergency room, from greeting
					to financing.}
				\item{Assisted nurses, and helped patients and visitors to solve non-treatment
					issues.}
				\item{Maintained supplies, including food, beverage, linens, disposable medical
					supplies.}
			\end{tightemize}
		}

    \entry
    {01/10-05/12}
		{Teaching Assistant}
		{Biology Department, SUNY Binghamton}
    {
			\begin{tightemize}
				\item{Prepared experiments materials, designed and taught lab sections,
					demonstrated techniques.}
				\item{Held weekly office hours, graded all associated materials.}
				\item{Guided students' group research project and evaluated
					presentation.}
				\item{Demonstrated proficiency at computer aided teaching and research tools and
					the web search engines.}
			\end{tightemize}
		}

\end{entrylist}
