\section{Projects}
\begin{entrylist}
	\entry
		{09/14-03/14}
		{Master paper project: opioid receptor signaling and its role in cancer
			progression}
		{}
		{
			\begin{tightemize}
				\item{Discussed conflicting research findings by studying more than 50 BioMedical
					literatures.}
			\end{tightemize}
		}
	\entry
		{02/12-05/12}
		{Business Plan of Biomedical Start-up Company}
		{}
		{
			\begin{tightemize}
				\item{Created a business plan for biomedical start-up FyreSaw
					Rhythm, which develops an innovative cardiac device to treat atrial
					fibrillation by surgery.}
				\item{Worked in a team in creative thinking on the idea.}
				\item{Composed the business model, exit strategy, and financials
					sections of the business plan.}
			\end{tightemize}
		}
	\entry
		{02/11-05/11}
		{Dynamic modeling of PI3K/Akt signaling induced by mu opioid receptor}
		{}
		{
			\begin{tightemize}
				\item{Obtained protein immunoblots data from my independent laboratory project
					conducted on human cancer cells, and applied it for the configuration of
					modeling.}
				\item{Designed and graphed a dynamic Model in Mathematica, simulating activity
					status and expression of multiple messenger molecules involved in this
					signaling process.}
			\end{tightemize}
		}
	\entry
		{09/09-01/10}
		{Data mining of microarray database in search of biomarker candidates}
		{}
		{
			\begin{tightemize}
				\item{Designed a Python program used to search GSO database for cancer
					biomarkers, potentially leading to metastasis of breast cancer, prostate
					cancer, and lung cancer.}
				\item{Presented the primary outcome in annual Binghamton University biology
					department seminar.}
			\end{tightemize}
		}
\end{entrylist}
